Measuring Individual Partisan Harm in Redistricting

### 2021-09-02 paper/paper.Rmd
try paragraph on why no global

*(Need some explanation as to why we are dropping the global measure at this point. B/c it boils down to a difference in seats?)*

>>>>

Harm is defined using the local, not global, utility measure, because inherently, global utility (and thus harm) will be constant for all voters of a particular party.
In fact, a harm measure defined analogously using global utility would essentially be a difference in seats won by a voter's party between plans $q$ and $\tilde q$ (the exact form would be affected by the function $g$).
This measure is not particularly interesting, and nor is it novel, being a standard measure of partisan harm in simulation-based redistricting litigation, up to a monotonic transformation **[CM: cite Rucho & LWV of PA]**.
**[CM: revisit ¶ based on NJ findings].**
